---
title: "Non-Standard Aesthetic: Rotation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Non-Standard Aesthetic: Rotation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(ggplot2)
library(ggsvg)
```

## Introduction

This example steps through the process of creating an SVG and mapping 
an SVG characteristic into a ggplot2 aesthetic.


ggplot2 aesthethics are not limited to colour, fill, size etc.

*Anything* in SVG can be used as a target for an aesthetic mapping.

In this example the **rotation** of an SVG arrow is controlled via a value in 
a data.frame.


Overview:

1. Introduce parameters with [glue](https://cran.r-project.org/package=glue) syntax, 
   using double curly braces `{{}}`
2. Set the defaults for these parameters using `geom_point_svg(..., defaults = list(...))`
3. Use these parameters as aesthetics
4. Add an appropriate `scale_svg_*()` to inform ggplot2 how to map values to 
   this parameter (which it will then insert into the SVG text)



#### Define the base SVG

```{r fig.height=1.5}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Generic SVG arrow
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
arrow_text <- '
<svg viewBox="0 0 100 100">
  <g transform="rotate(45 50 50)">
    <line x1="10" y1="50" x2="90" y2="50" stroke="black" stroke-width="2" />
    <line x1="70" y1="30" x2="90" y2="50" stroke="black" stroke-width="2" />
    <line x1="70" y1="70" x2="90" y2="50" stroke="black" stroke-width="2" />
  </g>
</svg>
'

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Draw the arrow
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
svg <- svg_to_rasterGrob(arrow_text)
grid::grid.newpage()
grid::grid.draw(svg)
```

#### Create parameterised SVG

In order to create a responsive SVG that has values dynamically mapped
in `ggplot2`, add named parameters in place of values in the SVG text.

In this example the SVG transform to rotate the arrow is `rotate(45 50 50)`
and this has been parameterised to `rotate({{angle}} 50 50 )`.


```{r fig.height=1.5}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# SVG arrow with controllable rotation angle
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
arrow_text <- '
<svg viewBox="0 0 100 100">
  <g transform="rotate({{angle}} 50 50)">
    <line x1="10" y1="50" x2="90" y2="50" stroke="black" stroke-width="2" />
    <line x1="70" y1="30" x2="90" y2="50" stroke="black" stroke-width="2" />
    <line x1="70" y1="70" x2="90" y2="50" stroke="black" stroke-width="2" />
  </g>
</svg>
'

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Test the rotation is changed as 'angle' is changed
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
angle <- -30
final_svg <- glue::glue(arrow_text, .open = "{{", .close = "}}")


#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Draw the rotated arrow
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
svg <- svg_to_rasterGrob(final_svg)
grid::grid.newpage()
grid::grid.draw(svg)
```


#### Create a plot with rotatable SVG arrow

```{r fig.width = 6, fig.height=4}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Create a plausible vector field
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
set.seed(13)
value <- 360 * as.vector(ambient::normalise(ambient::noise_perlin(c(10, 10))))
data  <- cbind(expand.grid(x=1:10, y=1:10), value)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Use 'value' to control the arrow angle
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
ggplot(data) + 
  geom_raster(aes(x, y, fill = value)) + 
  geom_point_svg(
    aes(x, y, angle = I(value)), 
    svg = arrow_text,
    size = 10,
    defaults = list(angle = 0)
  ) + 
  theme_bw() +
  theme(legend.position = 'none') + 
  scale_fill_viridis_c()
```
